### 2011-02-23 trunk/proposal/paper.tex
Added the diffs

From what we have explored till now, by quering Freebase we can get the
various property, value pairs of the entity that we have supplied in the form
of $TU$. In case the result is $\phi$, it suggests that we do not have
information for this particulat combination $TU$ and $AU_{i}$. Due to the
richness of the information in Freebase we can assume with a considerable degree of confidence
that this combination is untrue.

 \subsection {Rank the alternative statements based on the results
obtained by querying the ontologies}

\section{Finding relevance between the above two sets may be done in the
following manner}:

@@

%\bibliography{mybib}
%\bibliographystyle{alpha}

>>>>

From what we have explored till now, by quering Freebase we can get the
various property, value pairs of the entity that we have supplied in the form
of $TU$. In case the result is $\phi$, it suggests that we do not have
information for this particulat combination $TU$ and $AU_{i}$. Due to the
richness of the information in Freebase we can assume with a considerable degree of confidence
that this combination is untrue. This is one way verification, but in case of
non-null results, how do we filter and rank the results with the available set
of information is something we can not formulate at this stage with out further
exploration.

\subsection{Application of Machine learning algorithms}: 
Though application of machine learning algorithms like using Naive Bayesian,
neural network

@@

%\bibliography{mybib}
\bibliographystyle{alpha}
